### 2019-07-30 Thesis/pages/design.tex
Changes; - Added more content to design section

    \caption{Soundex mappings of letters to numbers}
\end{figure}

@@

\subsubsection{Metaphone}
\textbf{TODO}

\subsubsection{NYSIIS}
\textbf{TODO}

@@

>>>>

    \caption{Soundex mappings of letters to numbers}
\end{figure}
\textbf{TODO: Turn into a table}

@@

\subsubsection{NYSIIS}
The New York State Identification and Intelligence System (NYSIIS) Phonetic Code was created for use matching the phonetics of American names. However, due to it having embedded rules to handle word phonetics it would, again be applicable in this application. It allows for variable length codes and, thus, allows the applicability of the application to increase due to it not confronting the limited code issue of Soundex.

\subsubsection{Metaphone}
Metaphone was invented by Lawrence Philips in 1990\cite{philips1990hanging} in response to the deficienies in Soundex. It improves on Soundex by including information around inconsistency and variation in English spelling in an attempt to create a more accurate phonetic representation. Metaphone is arguably on the same level of ubiquity as that of Soundex with it finding itself implemented in languages such as big examples like PHP\cite{php}. Further work would involve the implementation of newer versions of Metaphone. Double Metaphone (2000) and Metaphone 3 (2009) claim to improve over the original version due to further research performed by Philips. The original version was chosen due to its historical wide spread usage alongside the case of Metaphone 3 being proprietary code and, therefore, under a paid licence.

\textbf{TODO: } Talk about why length of 10 was chosen.

@@

\textbf{TODO: } Do a sample conversions table

% List of papers assessing algorithms
%   - Analysis andComparative Study on Phonetic Matching Techniques
%   - Performance Evaluation of Phonetic Matching Algorithms on English Words and Street Names
%   - Study Existing Various Phonetic Algorithms and Designing and Development of a working model for the New Developed Algorithmand Comparison by implementing it with Existing Algorithm(s)

% Other alternatives:
% - Match Rating Approach
%   - Couldn't find an algorithm??
%
% - Caverphone

\textbf{TODO: } Need to justify why
